\PubListStart{Conference Papers}{C}

\PubItem
{Flex Attention: A Programming Model for Generating Optimized Attention Kernels} %Title
{\PubAuthorHighlight{Juechu Dong*}, Boyuan Feng*, Driss Guessous*, Yanbo Liang*, Horace He} %Author
{Proceedings of Machine Learning and Systems 7} % Conference.
{2025} % Year
{(MLSys '25)} %cmt
{} % DOI

\resumeItemListStart
\resumeItem{Develop a novel compiler-driven programming model that allows implementing the majority of attention variants in a few lines of idiomatic PyTorch code.}
\resumeItem{Optimize customizable attention kernels to provides 1.1x - 1.3x speedup compared to FlashAttn2 by lowering customizable attention into a fast Triton kernel + taking advantage of sparsity. }
\resumeItem{Adapt FlexAttention to efficiently support decoding, GQA and PagedAttention. }
% \resumeItem{Design, implement, optimize and benchmark for decoding \& GQA.}
\resumeItemListEnd

\PubItem
{Toleo: Scaling Freshness to Tera-scale Memory Using CXL and PIM} %Title
{\PubAuthorHighlight{Juechu Dong}, Jonathon Rosenblum, Satish Narayanasamy} %Author
{Proceedings of the 29th ACM International Conference on Architectural Support for Programming Languages and Operating Systems, Volume 4} % Conference.
{2024} % Year
{(ASPLOS '24)} %cmt
{10.1145/3622781.3674180} % DOI

\resumeItemListStart
\resumeItem{Scale trusted memory size from hundreds of MB to tens of TB by expanding the span of trusted from a single trusted processor to an entire platform including intelligent memories. }
\resumeItem{Design a new scheme of freshness protection that reduces the space requirement by 50x.}
\resumeItem{Reduce deployment cost by spacing sharing one intelligent memory device among multiple CPUs. }
\resumeItemListEnd


\PubItem
{mm2-gb: GPU Accelerated Minimap2 for Long Read DNA Mapping} %Title
{\PubAuthorHighlight{Juechu Dong}*, Xueshen Liu*, Harisankar Sadasivan, Sriranjani Sitaraman, Satish Narayanasamy} %Author
{Proceedings of the 15th ACM International Conference on Bioinformatics, Computational Biology, and Health Informatics} % Conference.
{2024} % Year
{(BCB '24\footnotemark)} %cmt
{} % DOI

\resumeItemListStart
\resumeItem{Accelerate computational intensive chaining step in the state-of-art long sequence mapping tool minimap2 using AMD GPU by 2.57-5.33x.}
\resumeItem{Optimize towards ultra long reads of 100k+ to accommodate genome sequencing technology trend.}
\resumeItem{Develop adaptive GPU scheduling algorithm to balance highly heterogeneous workload.}
\resumeItemListEnd

\PubListEnd

\footnotetext[1]{ACM-BCB is the flagship conference of the ACM SIGBio.}


\PubListStart{Journal Articles}{J}

\PubItem
{SECRET-GWAS: Confidential Computing for Population-Scale GWAS} %Title
{Jonathon Rosenblum, \PubAuthorHighlight{Juechu Dong}, Satish Narayanasamy} %Author
{Nature Computer Science} % Conference.
{2025} % Year
{} %cmt
{} % DOI

\resumeItemListStart
\resumeItem{Develop a thousand-core platform on Azure Confidential Computing to conduct multi-institutional GWAS on millions of patients in less than a minute.}
\resumeItem{Adapt Spark-based Hail genomic analysis framework to run on TEE under obliviousness requirement.}
\resumeItem{Parallelize GWAS computation on 1k cores to achieve near linear speedup.}
\resumeItemListEnd

\PubListEnd


\PubListStart{WorkShops}{W}

\PubItemCV
{mm2-gb: GPU Accelerated Minimap2 for Long Read DNA Mapping} %Title
{\PubAuthorHighlight{Juechu Dong}*, Xueshen Liu*, Harisankar Sadasivan, Sriranjani Sitaraman, Satish Narayanasamy} %Author
{The 1st Workshop on
Emerging Computer Systems Challenges and Applications in Biomedicine} % Conference.
{2024} % Year
{(BioSys \char`\@ ASPLOS '24)} %cmt
{} % DOI

\PubListEnd


\PubListStart{Poster}{P}
\PubItemCV
{Kraken: Hackable Triton Kernels for Computation and Multi-GPU Communication Fusion.} 
{\PubAuthorHighlight{Juechu Dong}*, Surya Subramanian} %Author
{PyTorch Conference} % Conference.
{2025} % Year
{} %cmt
{} % DOI

\PubListEnd

\PubListStart{Technical Reports \& Blogs}{T}

\PubItemCV
{FlexAttention Part II: FlexAttention for Inference} %Title
{\PubAuthorHighlight{Joy Dong}, Boyuan Feng, Driss Guessous, Joel Schlosser, Yanbo Liang, Horace He} %Author
{PyTorch Blogs} % Conference.
{Apr 2025} % Year
{} %cmt
{} % DOI

\PubItemCV
{FlexAttention: The Flexibility of PyTorch with the Performance of FlashAttention} %Title
{Team PyTorch: Driss Guessous, Yanbo Liang, \PubAuthorHighlight{Joy Dong}, Horace He} %Author
{PyTorch Blogs} % Conference.
{Aug 2024} % Year
{} %cmt
{} % DOI

\PubListEnd


\PubListStart{Under Submission / Preprints }{PP}

\PubItemCV
{HelmsDeep: Isolated Time-Based Defense for Storage Systems} %Title
{Jonathon Rosenblum, \PubAuthorHighlight{Juechu Dong}, Satish Narayanasamy} %Author
{submission to The 31st Symposium on Operating Systems Principles} % Conference.
{2025} % Year
{} %cmt
{} % DOI

\PubListEnd

