%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PROJECTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PUBLICATIONS} 
    \resumePubListStart
        % Project 1
        \pubItem
        {\textbf{Juechu Dong}, Jonathon Rosenblum, Satish Narayanasamy. "\textit{Toleo: Scaling Freshness to Tera-scale Memory Using CXL and PIM.}" In Proceedings of the 29th ACM International Conference on Architectural Support for Programming Languages and Operating Systems, Volume 4. 2024.}{ASPLOS '24} % Title
        \resumeItemListStart
        \resumeItem{Scale trusted memory size from hundreds of MB to tens of TB by expanding the span of trusted from a single trusted processor to an entire platform including intelligent memories. }
        \resumeItem{Design a new scheme of freshness protection that reduces the space requirement by 50x.}
        \resumeItem{Reduce deployment cost by spacing sharing one intelligent memory device among multiple CPUs. }
        \resumeItemListEnd
    
        % Project 2
        \pubItem
        {\textbf{Juechu Dong}*, Xueshen Liu*, Harisankar Sadasivan, Sriranjani Sitaraman, Satish Narayanasamy. \textit{"mm2-gb: GPU Accelerated Minimap2 for Long Read DNA Mapping."} In Proceedings of the 15th ACM International Conference on Bioinformatics, Computational Biology, and Health Informatics. 2024.  }{BCB '24\footnotemark} % Title
        \resumeItemListStart
        \resumeItem{Accelerate computational intensive chaining step in the state-of-art long sequence mapping tool minimap2 using AMD GPU by 2.57-5.33x.}
        \resumeItem{Optimize towards ultra long reads of 100k+ to accommodate genome sequencing technology trend.}
        \resumeItem{Develop adaptive GPU scheduling algorithm to balance highly heterogeneous workload.}
        \resumeItemListEnd


        \pubItem
        {\textbf{Juechu Dong*}, Boyuan Feng*, Driss Guessous*, Yanbo Liang*, Horace He. \textit{Flex Attention: A Programming Model for Generating Optimized Attention Kernels.} In Proceedings of Machine Learning and Systems 7. 2025. }{MLSys '25} % Title
        \resumeItemListStart
        \resumeItem{Develop a novel compiler-driven programming model that allows implementing the majority of attention variants in a few lines of idiomatic PyTorch code.}
        \resumeItem{Optimize customizable attention kernels to provides 1.1x - 1.3x speedup compared to FlashAttn2 by lowering customizable attention into a fast Triton kernel + taking advantage of sparsity. }
        \resumeItem{Adapt FlexAttention to efficiently support decoding, GQA and PagedAttention. }
        % \resumeItem{Design, implement, optimize and benchmark for decoding \& GQA.}
        \resumeItemListEnd

    \resumePubListEnd
    \footnotetext[1]{ACM-BCB is the flagship conference of the ACM SIGBio}


\section{PROJECTS IN PROGRESS} 
    \resumeSubHeadingListStart
        % Project 3
        \resumePaperHeading
        {SECRET-GWAS: Confidential Computing for Population-Scale GWAS} % Title
        {Nature Comp. Sci.} % Conference
        {J. Rosenblum, \underline{J. Dong}, S. Narayanasamy} % Authors
        {under review} % Status
        \resumeItemListStart
        \resumeItem{Develop a thousand-core platform on Azure Confidential Computing to conduct multi-institutional GWAS on millions of patients in less than a minute.}
        \resumeItem{Adapt Spark-based Hail genomic analysis framework to run on TEE under obliviousness requirement.}
        \resumeItem{Parallelize GWAS computation on 1k cores to achieve near linear speedup.}
        \resumeItemListEnd
        
        % Project 1
    
        % Project 2
        \resumePaperHeading
        {Timelocked Storage for Ransomware Defense} % Title
        {} % Conference
        {J. Rosenblum, \underline{J. Dong}, S. Narayanasamy} % Authors
        {under submission} % Status
        \resumeItemListStart
        \resumeItem{Propose a new randomeware defence mechanism that adds a strong layer of protection on top of conventional user creditial based security via a trusted storage system. }
        \resumeItem{Design simple yet efficient interface between the disk and the operating system to provide safe rollback. }
        \resumeItem{Optimize the secure storage system to achieve near zero access overhead. }
        \resumeItemListEnd
        
    \resumeSubHeadingListEnd